%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Tianxing Tian} & Email : \href{mailto:17212010035@fudan.edu.cn}{17212010035@fudan.edu.cn}\\
   & Mobile : +86-186-2178-9386 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Fudan University}{Shanghai, China}
      {Bachelor of Science in Software Engineering}{Sep. 2013 -- Jun. 2017}
    \resumeSubheading
      {University College Dublin}{Dublin, Ireland}
      {Visiting Scholar}{Jul. 2014 -- Aug. 2014}
    \resumeSubheading
      {Fudan University}{Shanghai, China}
      {Master of Science in Software Engineering}{Sep. 2017 -- Jun. 2020(expected)}
    
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Analysis and Security Lab, Fudan University}{Shanghai, CN}
      {Research Assistant}{Mar 2016 - Present}
      \resumeItemListStart
        \resumeItem{SinaBot}
          {SinaBot is an illustration recommendation system which is designed for recommending images for candidate articles and it's now in use for Sina Mobile. Be the first autor of the related paper and the paper is now under review.}
        \resumeItem{Article Search Engine}
          {A system which can search articles with keywords and character picture, winning the first prize of summer hathon hold by Data Analysis and Security Lab.}
          \resumeItem{Teaching Assistant-Java Programming, Object Oriented Programming(C++), Mutimedia Technique}
          {Design labs and projects for students. Resolve students' problem in study.}
          \resumeItem{Other}
          {Replicate MCNN(a text-image matching neural network) with Pytorch; Replicate FGSDMM(a text clustering method) in Java and improve its speed, undergraduate paper; classification of Chinese Calliagraphy fonts with neural network with Keras; onlince couseres about machine learning including cs231n, Deep Learning by ng, etc}
          
          \resumeItemListEnd

    \resumeSubheading
      {SAP Labs}{Shanghai, CN}
      {Test automation Engineer}{Sep 2016 - Apr 2017}
      \resumeItemListStart
      \resumeItem{Automatic Testing Framework}
      {Developed an automatic testing framework for SAP Business One and deployed the web system for users’ access.Created several modules and scripts for different testing purposes in JavaScript, C sharp, Java, Shell in order to test the whole business process from creating a new company account to settling accounts/simulating user actions automatically.}
      \resumeItemListEnd

    \resumeSubheading
      {Fudan University}{Shanghai, CN}
      {Undergraduate Student}{Sep 2014 - Jun 2017}
      \resumeItemListStart
        \resumeItem{Social Network Based High Frequency Trading Analysis}
          {Established trading models upon domain-specific opinion mining and social network analysis techniques.Selected as a demonstration program of Fudan’s Undergraduate Research Opportunities Program}


   \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Skills-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Language}
      {Frequent user of python and java, have expericen in C/C sharp/shell/java script/sql related/javascript/html/matlab}
    \resumeSubItem{Language}
      {Native speaker of Chinese, Fluent in written and spoken English.}
  \resumeSubHeadingListEnd

  %-----------Skills-----------------
\section{Activities}
\resumeSubHeadingListStart
  \resumeSubItem{Volunteer}
    {2018 IEEE International Conference on Big Data and Smart Computing}
  \resumeSubItem{Competition}
    {iShamrock Software Competition 2014/2016 1st runner-up award, mobile APP development competition hold by Fudan;bronze medal for 2014 Interdisciplinary Mathematical Contest}
\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
